---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggplot1

<!-- badges: start -->
[![R-CMD-check](https://github.com/hadley/ggplot1/actions/workflows/R-CMD-check.yaml/badge.svghttps://github.com/hadley/ggplot1/actions/workflows/R-CMD-check.yaml/badge.svghttps://github.com/hadley/ggplot1/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/hadley/ggplot1/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

ggplot1 is an update of ggplot, the package that preceded ggplot2. ggplot1 is mostly made available out of historical interest, to illustrate how my thinking about API design in R has evolved over the years. I've made a few minor tweaks to the package, mostly fixing small things that obscure the interesting parts of the API.
The most interesting thing about ggplot1 is that it was originally designed around the idea of function composition, so that you'd write code like this:

```{r}
#| eval: false
ggpoint(ggplot(mtcars, list(x = mpg, y = wt)))
```

I correct recognised that this was hard for people to read and write, but solved this problem in ggplot2 by overloading addition. In hindsight, this problem is solved generally by the pipe!

ggplot had 7 CRAN releases starting with 0.2.2 in April 2006, and finishing with 0.4.2 in October 2008.

## Installation

You can install ggplot1 from github with:

```R
# install.packages("pak")
pak::pak("hadley/ggplot1")
```

## Usage

```{r ex}
library(ggplot1)

mtcars |>
  ggplot(list(x = mpg, y = wt)) |>
  ggpoint()

mtcars |>
  ggplot(list(x = mpg, y = wt)) |>
  ggpoint(list(colour = gear)) |>
  scbrewer()
```
