---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggplot1

<!-- badges: start -->
[![R-CMD-check](https://github.com/hadley/ggplot1/actions/workflows/R-CMD-check.yaml/badge.svghttps://github.com/hadley/ggplot1/actions/workflows/R-CMD-check.yaml/badge.svghttps://github.com/hadley/ggplot1/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/hadley/ggplot1/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

ggplot1 is an update of ggplot, the package that preceded ggplot2. ggplot1 is mostly made available out of historical interest, to illustrate how my thinking about API design in R has evolved over the years.  I've made a few minor tweaks to the package, mostly fixing small things that obscure the interesting parts of the API.

ggplot had 7 CRAN releases starting with 0.2.2 in April 2006, and finishing with 0.4.2 in October 2008.

## Installation

You can install ggplot1 from github with:

```R
# install.packages("devtools")
devtools::install_github("hadley/ggplot1")
```

## Usage

```{r ex}
library(ggplot1)

mtcars |>
  ggplot(list(x = mpg, y = wt)) |>
  ggpoint()

mtcars |>
  ggplot(list(x = mpg, y = wt)) |>
  ggpoint(list(colour = gear)) |>
  scbrewer()
```
